Formalizing Abstract Rewriting

### 2025-02-09 Relations/Report.tex
abstract for FSCD

\title{Summer 2024 Report}
\author{Sam Arkle}
\date{\today}

@@

\newcommand{\down}[1]{{#1}{\downarrow}}
\begin{document}
\renewcommand{\arraystretch}{1.3}

\maketitle

@@

    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
          \to \big(\exists n \in \nat. s n \equiv a\big)\]

  \end{itemize}
\end{itemize}

>>>>

\title{Formalizing Abstract Rewriting}
% \title{Abstract Rewriting from a Constructive Viewpoint}
% \title{A Constructive View on Abstact Rewriting}
\author{Sam Arkle}
\date{\today}

@@

\newcommand{\down}[1]{{#1}{\downarrow}}

\begin{document}

\renewcommand{\arraystretch}{1.3}

\maketitle
\begin{abstract}
We formalize in the Agda proof assistant the main results about Abstract Reduction Systems (ARS) given in the standard reference [Terese].
% Our contribution can be viewed as a development of abstract rewriting using constructive logic.
% , and is part of a larger project aiming to develop a library of programming language theory in Agda. This application leads us to give special focus to concepts related to termination and confluence.
We define a taxonomy of concepts related to termination and confluence and investigate their relationships between each other and their classical counterparts.
We identify, and eliminate where possible, the use of classical logic in the proofs of standard ARS results.
% For example, the study of strong normalization leads us to multiple inequivalent
% formalizations of the notion of a well-founded relations, with subtle distinctions.
Our analysis leads to refinements and mild generalizations of classical termination and confluence criteria.
\end{abstract}

@@

    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
          \to \big(\exists n \in \nat. s n \equiv a\big)\]
  \end{itemize}
  \item When an element is not SN, it transitions to one which is not SN either.
  (Use in the proof of Theorem 1.2.3)
\end{itemize}
